Supplementary Material

### 2019-04-10 Paper/Paper.tex
Supplement Tables and Replace `XXXXX' s

\begin{figure}
\center
{\includegraphics[width=0.8\textwidth]{Figure1/Figure1.pdf}}
\caption{A. Schematic depiction of agent-based model components; blue/red denote tissue cells with/without mutations. Black arrows depict regulation of the cell fate in each cell cycle. Inset depicts major interactions between the immune system and tissue cells.
 %The parameters used in this model can be found in the Supplementary material. Unless otherwise stated, parameter values are assumed to be those found in the Supplement. \tcr{Thoughts on the wording here? Once I have the table, I will use the name of that table.}
B. A representation simulation of one patient. The model parameter values used can be found in XXXXX. 
The inflammation cycling scheme is represented above the patient dynamics. The vertical dashed line denotes the end of the warmup period. Mut: mutated cells; Mes: mesenchymal cells. 
C. Survival curve for one cohort of patients with the parameter values given in Table XXXXX. }
\label{fig:ModelIntro}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure2/Figure2.jpg}}
\caption{Sensitivity analysis of model parameters, determined via the global Morris one-step-at-a-time method. $\mu^*$ denotes the XXXXXX}
\label{fig:MOAT}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure3/Figure3.pdf}}
\caption{Effects of mesencymal cell properites on the time to cancer. Trajectories of one patient per cohort from warmup period ([-1000,0]) to 2000 cell cycles, for $\Delta_\text{MIE}$ (A); $\Delta_\text{MGA}$ (B); and $\tau_\text{Treg}$, Treg TGF-$\beta$ (C). 
D. Survival curves corresponding to changes in MIE (A) for a patient cohort of size XXXXX; shaded region represents XXXXXX. 
E. Survival curves for patient cohort corresponding to changes in MGA (B).
F. Survival curves for patient cohort corresponding to changes in Treg TGF-$\beta$ (C). 
%% \color{red} Cox regression or KM test statistics to be computed to demonstrate the significance of this claim.
}
\label{fig:FirstSurvivalCurves}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.9\textwidth]{Figure4/Figure4.pdf}}
\caption{Effects of inflammation on the time to cancer under different cycling schemes. A-B. As MIE varies, survival curves (each of XXXX patients)  and corresponding bar plots to summarize the mean Time to Cancer for each cohort are shown. C-D. As MGA varies, survival curves  and corresponding bar plots to summarize the mean time to cancer for each cohort are shown.}
\label{fig:VaryINFL_and_MesPars}
\end{figure}

>>>>

\begin{figure}
\center
{\includegraphics[width=0.8\textwidth]{Figure1/Figure1.pdf}}
\caption{A. Schematic depiction of agent-based model components; blue/red denote tissue cells with/without mutations. Black arrows depict regulation of the cell fate in each cell cycle. Inset depicts major interactions between the immune system and tissue cells.
 %The parameters used in this model can be found in the Supplementary material. Unless otherwise stated, parameter values are assumed to be those found in the Supplement. \tcr{Thoughts on the wording here? Once I have the table, I will use the name of that table.}
B. A representative simulation of one patient. The model parameter values used can be found in Supplementary Table 2. 
The inflammation cycling scheme is represented above the patient dynamics. The vertical dashed line denotes the end of the warmup period. Mut: mutated cells; Mes: mesenchymal cells. 
C. Survival curve for one cohort of patients with the parameter values given in Supplementary Table 2. }
\label{fig:ModelIntro}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure2/Figure2.jpg}}
\caption{Sensitivity analysis of model parameters, determined via the global Morris one-step-at-a-time method. $\mu^*$ denotes the average absolute change in Time to Cancer when the parameter is varied.}
\label{fig:MOAT}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure3/Figure3.pdf}}
\caption{Effects of mesencymal cell properites on the time to cancer. Trajectories of one patient per cohort from warmup period ([-1000,0]) to 2000 cell cycles, for $\Delta_\text{MIE}$ (A); $\Delta_\text{MGA}$ (B); and $\tau_\text{Treg}$, Treg TGF-$\beta$ (C). 
D. Survival curves corresponding to changes in MIE (A) for a patient cohort of size 1000; shaded region represents the 95\% confidence interval for the evaluated function. 
E. Survival curves for patient cohort corresponding to changes in MGA (B).
F. Survival curves for patient cohort corresponding to changes in Treg TGF-$\beta$ (C). 
%% \color{red} Cox regression or KM test statistics to be computed to demonstrate the significance of this claim.
}
\label{fig:FirstSurvivalCurves}
\end{figure}

@@

\begin{figure}
\center
{\includegraphics[width=0.9\textwidth]{Figure4/Figure4.pdf}}
\caption{Effects of inflammation on the time to cancer under different cycling schemes. A-B. As MIE varies, survival curves (each of 200 patients)  and corresponding bar plots to summarize the mean Time to Cancer for each cohort are shown. C-D. As MGA varies, survival curves  and corresponding bar plots to summarize the mean time to cancer for each cohort are shown.}
\label{fig:VaryINFL_and_MesPars}
\end{figure}

### 2019-04-10 Paper/Supplement/Supplement.tex
Added condensed table to paper; made edits to MOAT section
Supplement Tables and Replace `XXXXX' s

\begin{center}
 \begin{longtable}{|| c | c||} 
 \hline
 Name & Description  \\ [0.5ex] 
 \hline\hline
  & RP Cancer Line   \\ 
 \hline
$\Delta_\text{MIE}$ &  \\
 \hline
 $\Delta_\text{MGA}$ & MGA    \\
 \hline
&  INFL High Duration   \\
 \hline
 & INFL Low Duration    \\
 \hline
& Mes Threshold   \\
 \hline
 $p$ & proliferation rate of tissue cells \\ 
 \hline
 $d_C$  & death rate of tissue cells \\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell\\
 \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation\\
 \hline
 $E_\text{NK}$ & rate of NKs clearing mutants  \\
  \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants \\
  \hline
  & increased NK efficacy during high inflammation  \\
  \hline
  & increased CTL efficacy during high inflammation  \\
  \hline
  & increased Treg efficacy during high inflammation  \\
  \hline
  $\sigma_\text{NK}$ & NK source rate \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell \\ 
  \hline
   & increased NK source rate during high inflammation  \\
  \hline
   & increased CTL source rate during high inflammation  \\
  \hline
   & increased Treg source rate during high inflammation  \\
  \hline
  & maximum initial mutation damage after warmup  \\
  \hline
  & increase in probability to mutate for non-mutating proliferating cells  \\
  \hline
  $\Delta_A$ & mutant cells decreased apoptosis  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation  \\
  \hline
  $k_\text{EMT}$ & EMT/MET rate  \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive \\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells\\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg\\
  \hline
\end{longtable}
\end{center}

\newpage

\begin{center}
 \begin{longtable}{||c | p{10cm} | c||} 
 \hline
 Name & Description & Value  \\ [0.5ex] 
 \hline\hline
 RP Cancer Line & When proportion of mutant cells reaches this number, then cancer is declared & 0.5  \\ 
 \hline
 MIE & (mesenchymal immune evasion) proportional decrease of probability immune cells clear mutated mesenchymal cells & 0.6  \\
 \hline
 MGA & (mesenchymal growth arrest) proportional decrease of probability mesenchymal cells proliferate; this decreased probability is accompanied and an equal and opposite increase in probability of rest & 0.2  \\
 \hline
 INFL High Duration & Number of consecutive cell cycles a patient will experience high inflammation before returning to a low inflammatory state & 30  \\
 \hline
INFL Low Duration & Number of consecutive cell cycles a patient will experience low inflammation before returning to a high inflammatory state & 30  \\
 \hline
Mes Threshold & the threshold EMT score above which a cell is labeled mesenchymal and below which it is labeled epithelial & 0.7 \\
 \hline
 p & weight of a cell proliferating during a cell cycle & 0.28 \\ 
 \hline
 d & weight of a cell dying during a cell cycle & 0.14 \\
 \hline
 $N_{00}$ & EC50 term for Hill functions describing likelihood of cytotoxic immune cells locating mutated cells & 8\\
 \hline
 $N_0$ & EC50 term for Hill function describing negative feedback of total cell population on cell proliferation rates & 80 \\
 \hline
  NK Efficacy Low & weight of NK cell clearing mutated cells during low inflammation & 0.2 \\
  \hline
  Treg EC50 Low & EC50 term for Hill functions describing Treg-mediated inhibition of efficacy of cytotoxic immune cells during low inflammation & 5 \\
  \hline
  CTL Efficacy Low & weight of CTL cell clearing mutated cells during low inflammation & 4 \\
  \hline
  NK Efficacy Up & proportional increase of NK Efficacy Low during high inflammation & 2 \\
  \hline
  CTL Efficacy Up & proportional increase of CTL Efficacy Low during high inflammation & 3 \\
  \hline
  Treg Efficacy Up & during high inflammation, Treg EC50 is Treg EC50 Low / Treg Efficacy Up & 200 \\
  \hline
  NK Source Low & rate at which NK cells enter TME during low inflammation & 1.3 \\ 
  \hline
  CTL Recruitment Low & rate at which CTL cells are recruited after mutated cells are lysed during low inflammation & 100 \\ 
  \hline
  Treg Recruitment Low & rate at which Treg cells are recruited after mutated cells are lysed during low inflammation & 200 \\
  \hline
  NK Recruitment Up & proportional increase of NK source rate during high inflammation & 1 \\
  \hline
  CTL Recruitment Up & proportional increase of CTL recruitment rate during high inflammation & 1 \\
  \hline
   Treg Recruitment Up & proportional increase of Treg recruitment rate during high inflammation & 1 \\
  \hline
  $p_{mutation}$ Start & maximum probability of mutating after the warmup period ends & 1e-2 \\
  \hline
  $p_{mutation}$ & increase in probability of a cell mutating after it proliferates but does not mutate & 1e-4 \\
  \hline
  Apoptosis Down & proportional decrease in apoptosis weight for cells with apoptosis pathway mutated & 0.3 \\
  \hline
  Immune Evasion & proportional decrease in immune clearance weight for cells with immune pathway mutated & 0.48 \\
  \hline
  Proliferation Up & proportional increase in proliferation weight for cells with proliferation pathway mutation & 0.36 \\
  \hline
  $k_{EMT}$ & rate parameter controlling speed of EMT and MET & .01 \\
  \hline
  c & standard deviation of noise on TGF-$\beta$ received by each cell & 6 \\
  \hline
  TGFB Received EC50 & EC50 term for Hill function determining how much TGF-$\beta$ in TME enters a cell & 200 \\
  \hline
  TGFB Max & maximum amount of TGF-$\beta$ that can enter a cell from the TME during a cell cycle & 500 \\
  \hline 
  Mutant TGFB & amount of TGF-$\beta$ produced by each mutated cell each cycle & 5e-2 \\
  \hline
  Treg TGFB & amount of TGF-$\beta$ produced by each Treg cell each cycle & 5e-1 \\
  \hline
\end{longtable}
\end{center}

\newpage

 \begin{longtable}{||c | c | c | c | c | c | c | c | c | c ||} 
 \hline
 Name & Base Value & Single Patient & Survival Curve & Vary MIE & Vary MGA & Vary Treg TGFB & Vary MIE and INFL & Vary MGA and INFL & Heat Map\\ [0.5ex] 
 \hline\hline
 RP Cancer Line &  0.5 &  \\ 
 \hline
 MIE  & 0.6 & 0.9 & 0.4-0.9 & 0.7 & 0.5 & 0.9 \\
 \hline
 MGA & 0.2 & & 0.1-0.4 & 0 & 0.2 & 0 \\
 \hline
 INFL High Duration  & 30 & & & & 60 & & & & 60 \\
 \hline
INFL Low Duration  & 30  \\
 \hline
Mes Threshold & 0.7 \\
 \hline
 p  & 0.28 \\ 
 \hline
 d  & 0.14 \\
 \hline
 $N_{00}$  & 8\\
 \hline
 $N_0$  & 80 \\
 \hline
  NK Efficacy Low  & 0.2 & 10 & & 10 & 10 & 10 & 10 & 10 & 10 \\
  \hline
  Treg EC50 Low & 5 & & & & & 2.5 \\
  \hline
  CTL Efficacy Low  & 4 & 200 & & 200 & 200 & 200 & 200 & 200 & 200\\
  \hline
  NK Efficacy Up & 2 & & & & 1.2 & & & &  1.2 \\
  \hline
  CTL Efficacy Up & 3 & & & & 3 & & & &  3\\
  \hline
  Treg Efficacy Up  & 200 & & & & 10& & & &  10\\
  \hline
  NK Source Low  & 1.3 \\ 
  \hline
  CTL Recruitment Low  & 100 \\ 
  \hline
  Treg Recruitment Low  & 200 \\
  \hline
  NK Recruitment Up & 1 & & & & & 3\\
  \hline
  CTL Recruitment Up & 1 & & & & & 3\\
  \hline
   Treg Recruitment Up & 1 & & & & & 5\\
  \hline
  $p_{mutation}$ Start & 1e-2 \\
  \hline
  $p_{mutation}$ & 1e-4 \\
  \hline
  Apoptosis Down & 0.3 \\
  \hline
  Immune Evasion & 0.48 \\
  \hline
  Proliferation Up & 0.36  \\
  \hline
  $k_{EMT}$  & .01 \\
  \hline
  c & 6 \\
  \hline
  TGFB Received EC50 & 200 \\
  \hline
  TGFB Max & 500 & 700 & & & & & &  & 700\\
  \hline 
  Mutant TGFB & 5e-2 & & & & & 0.5\\
  \hline
  Treg TGFB & 5e-1 \\
  \hline
\end{longtable}

>>>>

\begin{center}
 \begin{longtable}{|| c | c||} 
 \hline
 Name & Description  \\ [0.5ex] 
 \hline
 $p$ & proliferation rate of tissue cells \\ 
 \hline
 $d_C$  & death rate of tissue cells \\
 \hline
$\Delta_\text{MIE}$ &  mesenchymal immune evasion \\
 \hline
 $\Delta_\text{MGA}$ & mesenchymal growth arrest    \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation\\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell\\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants \\
  \hline
  $\sigma_\text{NK}$ & NK source rate \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate  \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives  \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive \\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells\\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg\\
  \hline
\end{longtable}
\end{center}

\begin{center}
 \begin{longtable}{|| c | p{7cm} | c | c ||} 
 \hline
 Name & Description & INFL Low Value & INFL High Value  \\ [0.5ex] 
 \hline\hline
  $p$ & proliferation rate of tissue cells & 0.28 & \\ 
 \hline
 $d_C$  & death rate of tissue cells & 0.14 & \\
 \hline
$\Delta_\text{MIE}$ &  MIE & 0.6 & \\
 \hline
 $\Delta_\text{MGA}$ & MGA  & 0.2 &  \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis & 0.3 &  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion & 0.48 &  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation & 0.36 &  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation & 80 & \\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell & 8 & \\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions & 5 & 0.025  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has & 200 & \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants & 10 & 30  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants & 200 & 600 \\
  \hline
  $\sigma_\text{NK}$ & NK source rate & 1.3 &  \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell & 100 & \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell & 200 & \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate & 0.01 & \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives & 6 & \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive & 500 &\\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells & 0.05 & \\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg & 0.5 & \\
  \hline
  & RP Cancer Line  & 0.5 &  \\ 
 \hline
&  INFL High Duration & 30&   \\
 \hline
 & INFL Low Duration &30 &   \\
 \hline
& Mes Threshold & 0.7 &    \\
 \hline
  & maximum initial mutation damage after warmup  & 0.01 &\\
  \hline
  & increase in probability to mutate for non-mutating proliferating cells & 0.0001 & \\
  \hline
\end{longtable}
\end{center}

%\newpage
%
%
% \begin{longtable}{||c | c | c | c | c | c | c | c | c | c ||} 
% \hline
% Name & Base Value & Single Patient & Survival Curve & Vary MIE & Vary MGA & Vary Treg TGFB & Vary MIE and INFL & Vary MGA and INFL & Heat Map\\ [0.5ex] 
% \hline\hline
% RP Cancer Line &  0.5 &  \\ 
% \hline
% MIE  & 0.6 & 0.9 & 0.4-0.9 & 0.7 & 0.5 & 0.9 \\
% \hline
% MGA & 0.2 & & 0.1-0.4 & 0 & 0.2 & 0 \\
% \hline
% INFL High Duration  & 30 & & & & 60 & & & & 60 \\
% \hline
%INFL Low Duration  & 30  \\
% \hline
%Mes Threshold & 0.7 \\
% \hline
% p  & 0.28 \\ 
% \hline
% d  & 0.14 \\
% \hline
% $N_{00}$  & 8\\
% \hline
% $N_0$  & 80 \\
% \hline
%  NK Efficacy Low  & 0.2 & 10 & & 10 & 10 & 10 & 10 & 10 & 10 \\
%  \hline
%  Treg EC50 Low & 5 & & & & & 2.5 \\
%  \hline
%  CTL Efficacy Low  & 4 & 200 & & 200 & 200 & 200 & 200 & 200 & 200\\
%  \hline
%  NK Efficacy Up & 2 & & & & 1.2 & & & &  1.2 \\
%  \hline
%  CTL Efficacy Up & 3 & & & & 3 & & & &  3\\
%  \hline
%  Treg Efficacy Up  & 200 & & & & 10& & & &  10\\
%  \hline
%  NK Source Low  & 1.3 \\ 
%  \hline
%  CTL Recruitment Low  & 100 \\ 
%  \hline
%  Treg Recruitment Low  & 200 \\
%  \hline
%  NK Recruitment Up & 1 & & & & & 3\\
%  \hline
%  CTL Recruitment Up & 1 & & & & & 3\\
%  \hline
%   Treg Recruitment Up & 1 & & & & & 5\\
%  \hline
%  $p_{mutation}$ Start & 1e-2 \\
%  \hline
%  $p_{mutation}$ & 1e-4 \\
%  \hline
%  Apoptosis Down & 0.3 \\
%  \hline
%  Immune Evasion & 0.48 \\
%  \hline
%  Proliferation Up & 0.36  \\
%  \hline
%  $k_{EMT}$  & .01 \\
%  \hline
%  c & 6 \\
%  \hline
%  TGFB Received EC50 & 200 \\
%  \hline
%  TGFB Max & 500 & 700 & & & & & &  & 700\\
%  \hline 
%  Mutant TGFB & 5e-2 & & & & & 0.5\\
%  \hline
%  Treg TGFB & 5e-1 \\
%  \hline
%\end{longtable}
%
%
